\documentclass{article}

\begin{document}
	\begin{itemize}
		\item \textbf{\underline{Developer :  John Backus
		}}
	\item FORTRAN
	\item History
	\item It was developed by a team of programmers at IBM led by John Backus(Dec. 3 , 1924 –March 17,2007) in 1957. It is called FORTRAN ( Formula Translation)  because of how it is developed to enable easy translation of math formulas into code. John Backus made a proposal to his colleagues .When it was first released people were skeptical about it, eventually it quickly gained acceptance  . It was the first high-level language using compiler. It is now one of the oldest programming languages . it was developed with the intention of making a programming language which was simple to learn.
	\item   It made coding so much easy , programmers were able to focus more on execution than the process of debugging the code. FORTRAN also develop several dialects ( due to some modification of some programmers for their best interest. The ASS reviewed the problem then produced a version FORTRAN’66 then there was FORTRAN’77(1978) and the latest which is still in use till date FORTRAN’90(1991). It was a huge success since in the past programs were written in machine language or assembly language, which required the programmers to write instructions in binary or hexadecimal. Fortran is used for factory automation control, storm drainage design.
	\item IDE used Fortran – Eclipse- Photran , visual studio, simply Fortran, Plato. Etc.
	
	
	
	\end{itemize}
\end{document}
	